---
title: "PTP1-MPS-Overview"
author: "Catherine Wong"
output: 
  html_document: 
    keep_md: yes
---
This is an overview of Phase 1 Microplastics Data for Pollution Tracker

```{r, echo = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, tidy = TRUE) 
```

### Data  

```{r, echo = FALSE}
library("dplyr")
library("tidyverse")
library("stringr")
library("ggplot2")
library("forcats")
library("knitr")
library("kableExtra")
opts_knit$set(root.dir = "C:/Users/Cath Wong/Desktop/PTP/PTP1 Data/Data")
```


```{r, results='hold', echo = FALSE}
datS <- read.csv("ptp1_sediments_R_Extraction_FTIR_Results_CW.csv", na.strings="") %>% 
  select(site, area, shape, color, long_axis, short_axis, susp_plastic, ftir, final_name_particle, origin_particle, category_particle, group_particle, ftir_particle_id) %>% 
  filter(!area %in% c("remove"))

datM <- read.csv("ptp1_mussels_R_Extraction_FTIR_Results_CW.csv", na.strings="") %>% 
  filter(shape != "0") %>% 
  select(site, area, shape, color, long_axis, short_axis, susp_plastic, ftir, final_name_particle, origin_particle, category_particle, group_particle, ftir_particle_id) 

wts <- read.csv("ptp1_mussels_extraction_data.csv", na.strings="") %>% 
  select(site, sample, tis_ww, microscope_done) %>% 
  filter(microscope_done=="y")

sub <- kable((datS[148:158, ])) %>% 
  kable_styling(bootstrap_options = "bordered")
sub
```


### Summary
#### __*Number of sites*__
```{r Calculate number of sites, number of particles, number of plastics, include = FALSE}
SMsites_table <- semi_join(datS, datM, by = "site")
SMsites <- unique(SMsites_table$site)
```

There are __`r length(unique(datS$site))`__ sediment sites and __`r length(unique(datM$site))`__ mussel sites  
There are __`r length(SMsites)`__ sites that sampled both sediment and mussels        
  
Each sediment sample is 50g of dry sediment per site.
Each mussel sample is 8 blue mussels per site.


__IN SEDIMENT:__  
-	Out of `r sum(datS$susp_plastic == "yes")` suspected mps, 
`r (sum(datS$ftir == "yes" & datS$susp_plastic == "yes")/sum(datS$susp_plastic == "yes"))*100` % were FTIR’d and 
`r datS %>% tally(category_particle == "plastic" & susp_plastic == "yes")` of those suspected were confirmed to be plastic 
```{r MPS Abundance in Sediment, echo = FALSE}
corr <- datS %>% 
  group_by(site) %>% 
  tally (ftir=="no" & susp_plastic == "yes", name="suspNonFTIR") %>% 
  mutate(suspNonFTIRCorr = suspNonFTIR*0.24) 

mps_count_sed <- datS %>% 
  group_by(site) %>% 
  tally(category_particle=="plastic", name = "MPS_Count") %>% 
  mutate(MPS_Corr=MPS_Count+corr$suspNonFTIRCorr) %>% 
  mutate(MPS_CorrPerKG=MPS_Corr*20)
```
Average abundance was `r mean(mps_count_sed$MPS_CorrPerKG, na.rm=TRUE)` MP per kg dry weight sediment 


__IN MUSSELS:__  
-	Out of `r sum(datM$susp_plastic == "yes")` suspected mps, 
`r (sum(datM$ftir == "yes" & datM$susp_plastic == "yes")/sum(datM$susp_plastic == "yes"))*100` % were FTIR’d and 
`r datM %>% tally(category_particle == "plastic" & susp_plastic == "yes")` of those suspected were confirmed to be plastic 

```{r Average Abundance in Mussels, echo = FALSE}
corr_m <- datM %>% 
  group_by(site) %>% 
  tally (ftir=="no" & susp_plastic == "yes", name="suspNonFTIR") %>% 
  mutate(suspNonFTIRCorr = suspNonFTIR*0.24)

mps_count_mus <- datM %>% 
  group_by(site) %>% 
  tally(category_particle=="plastic", name = "MPS_Count") %>% 
  mutate(MPS_Corr=MPS_Count+corr_m$suspNonFTIRCorr) %>% 
  mutate(MPS_CorrPerMussel=MPS_Corr/8)

wts_av<- wts %>% 
  group_by(site) %>% 
  summarize(mean_wt = mean(tis_ww, na.rm=TRUE))

mps_count_mus_ww <- mps_count_mus %>% 
  full_join(wts_av, by="site") %>% 
  mutate(mps_ww = MPS_CorrPerMussel/mean_wt)
```

Average abundance was `r mean(mps_count_mus_ww$mps_ww, na.rm=TRUE)` MP or SMP per gram WW and 
`r mean(mps_count_mus$MPS_CorrPerMussel)`  MP per individual (N = `r nrow(mps_count_mus)`)


#### __*Particles count*__
```{r, echo = FALSE}
A <- sum(datS$susp_plastic != "no" | datS$ftir != "no") + sum(datM$susp_plastic != "no" | datM$ftir != "no")

B <- sum(datS$susp_plastic == "yes" & datS$ftir == "yes") + sum(datM$susp_plastic == "yes" & datM$ftir == "yes")

C <- sum(datS$susp_plastic == "yes") + sum(datM$susp_plastic == "yes")

Da <- datS %>% 
  filter(category_particle == "plastic") %>% 
  tally()
Db <- datM %>% 
  filter(category_particle == "plastic") %>% 
  tally()
D <- Da$n + Db$n

E <- sum(datS$ftir == "yes") + sum(datM$ftir == "yes")

dt <- matrix(c(A, E, B, C, D), ncol=1, byrow=TRUE) 
colnames(dt) <- c("Total") 
rownames(dt) <- c("# particles",  "# FTIR'd", "# suspected + FTIR", "# suspected","# confirmed plastic")

dt %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped",
                                      "bordered"), 
                full_width = F, 
                position = "left")
```
The "Correction factor" calculated is:  
confirmed plastic / suspected & FTIR'd = __`r (D/B)*100` %__

I can now use this 24% value to estimate the number of plastics that were __suspected but not FTIR'd__ particles

* This will only work if you are applying this % to a large n, because this value was also calculated from large n. It cannot be indicative of the amount of plastics if the n is small.  

__Question:__ How to incorporate "false positives" and "false negatives". Should each individual have their own false negatives rate and it must be below 10%?

__Question:__ How do you know at what population size you COULD use this correction %? Does it even make sense to use this method at all? Is there a statistical test we could use?

### Shape & Plastic Type & Size Frequency  {.tabset .tabset-fade .tabset-pills}
#### Shape
Frequency of shapes 

```{r, echo = FALSE}
datScount <- datS %>% 
  filter(susp_plastic == "yes") %>% 
  count(shape) %>% 
  mutate(freq = n / sum(n)*100)
# datScount$group_particle <- fct_explicit_na(datScount$group_particle, na_level = "not_analyzed") 
  
ggplot(datScount, aes(x = reorder(shape, -n), y = n)) +
  geom_histogram(stat = "identity") +
  ggtitle("Frequency of Particles in Sediment") +
  theme(axis.text.x = element_text(angle =45 , vjust = 0.9, hjust = 0.9)) +
  labs(x="Suspected Plastic Shape", y="Count in All Sediment Samples") +
  geom_text(aes(y=n, label=n, vjust=-0.5))
```
  
In suspected microplastics found in sediment, `r datScount[1, "freq"]` % were fibres, `r datScount[3, "freq"]`% were fragments, `r datScount[6, "freq"]`% were sheets, `r datScount[5, "freq"]`% were foam,  `r datScount[4, "freq"]`% were granule.

```{r, echo = FALSE}
datMcount <- datM %>% 
  filter(susp_plastic == "yes") %>% 
  count(shape)%>% 
  mutate(freq = n / sum(n)*100)
# datMcount$group_particle <- fct_explicit_na(datMcount$group_particle, na_level = "not_analyzed") 
  
ggplot(datMcount, aes(x = reorder(shape, -n), y = n)) +
  geom_histogram(stat = "identity") +
  ggtitle("Frequency of Particles in Mussels") +
  theme(axis.text.x = element_text(angle =45 , vjust = 0.9, hjust = 0.9)) +
  labs(x="Suspected Plastic Shape", y="Count in All Mussel Samples") +
  geom_text(aes(y=n, label=n, vjust=-0.5))

```
In suspected microplastics found in mussels, `r datMcount[1, "freq"]` % were fibres, `r datMcount[3, "freq"]`% were fragments, `r datMcount[8, "freq"]`% were sheets, `r datMcount[4, "freq"]`% were granule.

#### Colour
__Colour Frequency in Sediment__
```{r, echo = FALSE}
datScolor <- datS %>% 
  filter(susp_plastic == "yes") %>% 
  count(color, na.rm=TRUE) %>% 
  mutate(freq = n / sum(n)*100)

ggplot(datScolor, aes(x = reorder(color, -n), y = n)) +
  geom_histogram(stat = "identity") +
  ggtitle("Frequency of Colours in Sediment") +
  theme(axis.text.x = element_text(angle =45 , vjust = 0.9, hjust = 0.9)) +
  labs(x="Colour", y="Count in All Sediment Samples") +
  geom_text(aes(y=n, label=n, vjust=-0.5))
```

__Colour Frequency in Mussel__
```{r, echo = FALSE}
datMcolor <- datM %>% 
  filter(susp_plastic == "yes") %>% 
  count(color, na.rm=TRUE) %>% 
  mutate(freq = n / sum(n)*100)

ggplot(datMcolor, aes(x = reorder(color, -n), y = n)) +
  geom_histogram(stat = "identity") +
  ggtitle("Frequency of Colours in Mussels") +
  theme(axis.text.x = element_text(angle =45 , vjust = 0.9, hjust = 0.9)) +
  labs(x="Colour", y="Count in All Mussel Samples") +
  geom_text(aes(y=n, label=n, vjust=-0.5))
```

### Calculating MPS Estimates for every site
* __Question:__ Can we make *any* estimates based on the data? Or only from what has been observed and confirmed?

```{r MPS COUNTS, echo = FALSE}
### Sediment
corr <- datS %>% 
  group_by(site) %>% 
  tally (ftir=="no" & susp_plastic == "yes", name="suspNonFTIR") %>% #Tallies suspected but not FTIR'd particles
  mutate(suspNonFTIRCorr = suspNonFTIR*0.24) #Multiply suspected by correction factor "24% correct"

mps_count_sed <- datS %>% 
  group_by(site) %>% 
  tally(category_particle=="plastic", name = "MPS_Count") %>% 
  mutate(MPS_Corr=MPS_Count+corr$suspNonFTIRCorr) %>% 
  mutate(MPS_CorrPerKG=MPS_Corr*20) %>% 
  mutate(area = datS$area[match(site, datS$site)]) 

### Mussels
corr_m <- datM %>% 
  group_by(site) %>% 
  tally (ftir=="no" & susp_plastic == "yes", name="suspNonFTIR") %>% 
  mutate(suspNonFTIRCorr = suspNonFTIR*0.24)

mps_count_mus <- datM %>% 
  group_by(site) %>% 
  tally(category_particle=="plastic", name = "MPS_Count") %>% 
  mutate(MPS_Corr=MPS_Count+corr_m$suspNonFTIRCorr) %>% 
  mutate(MPS_CorrPerMussel=MPS_Corr/8) %>% 
  mutate(area = datM$area[match(site, datM$site)]) 

kable(head(corr)) %>% 
        kable_styling(bootstrap_options = c("striped",
                                            "bordered"),
  full_width = F, position = "float_left")

kable(head(mps_count_sed)) %>% 
        kable_styling(bootstrap_options = c("striped",
                                            "bordered"),
  full_width = F, position = "right")
```

### Calculating MPS Estimates for every Area  {.tabset .tabset-fade .tabset-pills}
#### All areas
* __Next step:__ Determine significant differences between areas  
    + If estimates cannot be made, then there isn't a way to determine if areas are significantly different
*Consider changing MPS count from "per mussel" to "per tissue wet wt"

```{r MPS ESTIMATES BY AREA Sediment, echo = FALSE, out.width="65%"}
### Sediment
area_total <- mps_count_sed %>% 
  group_by(area) %>% 
  tally() %>% 
  mutate(label = paste0("n=", n))

area_means <- mps_count_sed %>% 
  group_by(area) %>% 
  summarise(
    mean = mean(MPS_CorrPerKG),
    se = sd(MPS_CorrPerKG, na.rm=TRUE)/sqrt(length(MPS_CorrPerKG))
  ) %>% 
  full_join(area_total, by="area")

area_means[is.na(area_means)] <- 0

kable(head(area_means)) %>%
    kable_styling(bootstrap_options = c("striped", "condensed", "bordered"),
                  position= "float_right",
                  full_width = F)
    
plot_area_means <- ggplot(area_means, aes(x = area, y = mean)) + 
  geom_bar(stat = "identity") +
  labs(x="Area", y="Microplastics Count Per 1kg Dry Sediment", tag="(a)") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
    width=0.2) +
  geom_text(aes(y=mean+se, label=label, vjust=-1)) +
  theme(axis.text.x = element_text(angle =45 , vjust = 1.15, hjust = 1.1))

plot_area_means
ggsave("plot_area_means.jpeg")     

```

```{r MPS ESTIMATES BY AREA Mussel, echo = FALSE, out.width="60%"}
### Mussels
area_total_m <- mps_count_mus %>% 
  group_by(area) %>% 
  tally() %>% 
  mutate(label = paste0("n=", n))

area_means_m <- mps_count_mus %>% 
  group_by(area) %>% 
  summarise(
        mean = mean(MPS_CorrPerMussel),
    se = sd(MPS_CorrPerMussel, na.rm=TRUE)/sqrt(length(MPS_CorrPerMussel))
  ) %>% 
  full_join(area_total_m, by="area")

area_means_m[is.na(area_means_m)] <- 0

kable(head(area_means_m)) %>%
    kable_styling(bootstrap_options = c("striped", "condensed", "bordered"),
                  position= "float_right",
                  full_width = F)

plot_area_means_m <- ggplot(area_means_m, aes(x = area, y = mean)) +
  geom_bar(stat = "identity") +
  labs(x="Area", y="Microplastics Count Per Mussel", tag="(b)") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
    width=0.2) +
  geom_text(aes(y=mean+se, label=label, vjust=-1)) +
  theme(axis.text.x = element_text(angle =45 , vjust = 1.15, hjust = 1.1))

plot_area_means_m 
ggsave("plot_area_means_m.jpeg")
```

#### Matched sites within areas
__Next step:__ Is there a relationship between sediment and mussels? (does not look like it at first glance. What test to use?)

```{r, echo = FALSE, out.width="65%"}
#### SEDIMENT 
mps_count_sed_match <- mps_count_sed %>% 
  filter(site %in% SMsites) 

area_total_match <- mps_count_sed_match %>% 
  group_by(area) %>% 
  tally() %>% 
  mutate(label = paste0("n=", n))

area_means_match <- mps_count_sed_match  %>% 
  group_by(area) %>% 
    summarise(
    se = sd(MPS_CorrPerKG, na.rm=TRUE)/sqrt(length(MPS_CorrPerKG)),
    mean = mean(MPS_CorrPerKG)
  ) %>% 
   full_join(area_total_match, by="area")

area_means_match[is.na(area_means_match)] <- 0

kable(head(area_means_match)) %>%
    kable_styling(bootstrap_options = c("striped", "condensed", "bordered"),
                  position= "float_right",
                  full_width = F)

plot_area_means_match <- ggplot(area_means_match, aes(x = area, y = mean)) +
  geom_bar(stat = "identity") +
  labs(x="Area", y="Microplastics Count Per 1kg Dry Sediment", tag="(a)") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
    width=0.2) +
  geom_text(aes(y=mean+se, label=label, vjust=-1)) +
  theme(axis.text.x = element_text(angle =45 , vjust = 1.15, hjust = 1.1))

plot_area_means_match
ggsave("plot_area_means_match.jpeg")
```


```{r, echo = FALSE, out.width="60%"}

#### MUSSELS ####
mps_count_mus_match <- mps_count_mus %>% 
  filter(site %in% SMsites) 

area_total_match_m <- mps_count_mus_match %>% 
  group_by(area) %>% 
  tally() %>% 
  mutate(label = paste0("n=", n))

area_means_match_m <- mps_count_mus_match %>% 
  group_by(area) %>% 
    summarise(
    se = sd(MPS_CorrPerMussel, na.rm=TRUE)/sqrt(length(MPS_CorrPerMussel)),
    mean = mean(MPS_CorrPerMussel)
  ) %>% 
 full_join(area_total_match_m, by="area")

area_means_match_m[is.na(area_means_match_m)] <- 0

kable(head(area_means_match_m)) %>%
    kable_styling(bootstrap_options = c("striped", "condensed", "bordered"),
                  position= "float_right",
                  full_width = F)

plot_area_means_match_m <- ggplot(area_means_match_m, aes(x = area, y = mean)) +
  geom_bar(stat = "identity") +
  labs(x="Area", y="Microplastics Count Per Mussel", tag="(b)") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
    width=0.2) +
  geom_text(aes(y=mean+se, label=label, vjust=-1)) +
  theme(axis.text.x = element_text(angle =45 , vjust = 1.15, hjust = 1.1))

plot_area_means_match_m
ggsave("plot_area_means_match_m.jpeg")
```

#### Mussels standardized for size
```{r, echo = FALSE}
wts_av <- wts %>% 
  group_by(site) %>% 
  summarize(mean_wt = mean(tis_ww, na.rm=TRUE))

mps_count_mus_ww <- mps_count_mus %>% 
  full_join(wts_av, by="site") %>% 
  mutate(mps_ww = MPS_Corr/mean_wt)

mps_area_mus_ww <- mps_count_mus_ww %>% 
  group_by(area) %>% 
  summarize(se = sd(mps_ww, na.rm=TRUE)/sqrt(length(mps_ww)),
    mean = mean(mps_ww, na.rm=TRUE))

plot_mus_area_ww <- ggplot(mps_area_mus_ww, aes(x = area, y = mean)) + 
                  labs(x="Area", y="Mean Microplastics Count Per GWW of Mussel Tissue") +
                  geom_bar(stat = "identity") +
                  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                  width=0.2) +
                  theme(axis.text.x = element_text(angle =45 , vjust = 1.15, hjust = 1.1))

plot_mus_area_ww

```

### Calculating Proportions  {.tabset .tabset-fade .tabset-pills}
Proportions are calculated from __confirmed / FTIR'd particles__.
n = number of plastic particles  
*__Note:__ n is quite low ... are these proportions meaningful?  
*The number of particles is too low for proportions to be meaningful, to make a conclusion for the entire area. 



#### All areas

```{r, Plastics in Sed, include = FALSE}
plastics <- datS %>% 
  droplevels() %>% 
  filter(final_name_particle != "na", category_particle == "plastic", area != "remove") %>% 
  group_by(area, group_particle, .drop = FALSE) %>%
  tally(name="Count") %>% 
  mutate(label = paste0("n=", sum(Count)))

plastics$group_particle <- factor(plastics$group_particle, levels = c("acrylic", "polyethylene",  "nylon", "polyester", "polystyrene", "rubber"))
  
plot_area_prop_plastypes  <- ggplot(plastics, 
                            aes(x = area,
                            y = Count,
                            fill = group_particle)) +
  ggtitle("Proportion of Plastic in Sediment") +
  labs(x="Site", y="Proportion", tag="(a)") +
  theme(axis.text.x = element_text(angle =45 , vjust = 1.15, hjust = 1.1))+
 # scale_fill_discrete(breaks=c("rubber", "acrylic", "polyethylene", "nylon", "polystyrene", "polyester"), name="Plastic Type") +
  geom_bar(stat="identity",
  position = "fill") +
  scale_fill_brewer(name = "Plastic Type", palette="Set2")  +
  scale_y_continuous(labels = scales::percent) +
  geom_text(aes(y=0.97, label=label, vjust=-1))

plot_area_prop_plastypes
```

```{r, Plastics in Mussel, include = FALSE}
plastics_m <- datM %>% 
  droplevels() %>% 
  filter(final_name_particle != "na", category_particle == "plastic", area != "remove") %>% 
  group_by(area, group_particle, .drop = FALSE) %>%
  tally(name="Count") %>% 
  mutate(label = paste0("n=", sum(Count)))

  
plastics_m$group_particle <- factor(plastics_m$group_particle, levels = c("acrylic", "polyethylene",  "nylon", "polyester", "polystyrene", "rubber"))
  
plot_area_prop_plastypes_m  <- ggplot(plastics_m, 
                            aes(x = area,
                            y = Count,
                            fill = group_particle)) +
  ggtitle("Proportion of Plastic in Mussel") +
  labs(x="Site", y="Proportion", tag="(b)") +
  theme(axis.text.x = element_text(angle =45 , vjust = 1.15, hjust = 1.1))+
 # scale_fill_discrete(breaks=c("rubber", "acrylic", "polyethylene", "nylon", "polystyrene", "polyester"), name="Plastic Type") +
  geom_bar(stat="identity",
  position = "fill") +
    scale_fill_brewer(name = "Plastic Type", palette="Set2")  +
  scale_y_continuous(labels = scales::percent) +
  geom_text(aes(y=0.97, label=label, vjust=-1))
  # coord_flip()
  
plot_area_prop_plastypes_m
```

#### Matched sites within areas
```{r, Plastics in matching Sed, include = FALSE}
plastics_match <- datS %>% 
  filter(site %in% SMsites) %>% 
  droplevels() %>% 
  filter(final_name_particle != "na", category_particle == "plastic", area != "remove") %>% 
  group_by(area, group_particle, .drop = FALSE) %>%
  tally(name="Count") %>% 
  mutate(label = paste0("n=", sum(Count)))

plastics_match$group_particle <- factor(plastics_match$group_particle, levels = c("acrylic", "polyethylene",  "nylon", "polyester", "polystyrene", "rubber"))
  
plot_area_prop_plastypes_match  <- ggplot(plastics_match, 
                            aes(x = area,
                            y = Count,
                            fill = group_particle)) +
  ggtitle("Proportion of Plastic in Sediment") +
  labs(x="Site", y="Proportion", tag="(a)") +
  theme(axis.text.x = element_text(angle =45 , vjust = 1.15, hjust = 1.1))+
 # scale_fill_discrete(breaks=c("rubber", "acrylic", "polyethylene", "nylon", "polystyrene", "polyester"), name="Plastic Type") +
  geom_bar(stat="identity",
  position = "fill") +
  scale_fill_brewer(name = "Plastic Type", palette="Set2")  +
  scale_y_continuous(labels = scales::percent) +
  geom_text(aes(y=0.97, label=label, vjust=-1))

plot_area_prop_plastypes_match
```

```{r Plastics in matching Mus, include = FALSE}
plastics_m_match <- datM %>% 
  filter(site %in% SMsites) %>% 
   droplevels() %>% 
  filter(final_name_particle != "na", category_particle == "plastic") %>% 
  group_by(area, group_particle, .drop = FALSE) %>%
  tally(name="Count") %>% 
  mutate(label = paste0("n=", sum(Count)))
  
plastics_m_match $group_particle <- factor(plastics_m_match $group_particle, levels = c("acrylic", "polyethylene", "nylon", "polyester"))
  
plot_match_area_prop_plastypes_m <- ggplot(plastics_m_match , 
                            aes(x = area,
                            y = Count,
                            fill = group_particle)) +
  ggtitle("Proportion of Plastic in Mussels") +
  labs(x="Site", y="Proportion", tag="(a)") +
  theme(axis.text.x = element_text(angle =45 , vjust = 0.9, hjust = 0.9))+
  scale_fill_discrete(breaks=c("acrylic", "polyethylene", "nylon", "polyester"), name="Plastic Type") +
  geom_bar(stat="identity",
  position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  geom_text(aes(y=0.97, label=label, vjust=-1))
  # coord_flip()
  
plot_match_area_prop_plastypes_m
```



### Proportions of Plastic Types and Shapes

```{r shapes, include=FALSE}
shapes_s <- datS %>% 
  group_by(shape) %>% 
  tally(name = "shapecount_s") 

shapes_m <- datM %>% 
  group_by(shape) %>% 
  tally(name = "shapecount_m") 

shape_sm <- full_join(shapes_s, shapes_m, by = "shape")
shape_sm[is.na(shape_sm)] <- 0

shape_sm_long <- shape_sm %>% 
  gather(key = "Matrix",
        value = "Count", 
        -c(shape)) 

shapeplot <- ggplot(shape_sm_long, 
  aes(x = Matrix, y = Count, 
  fill = factor(shape, levels = c("pellet", "sheet", "microbead","fragment", "fibre")))) +
  geom_bar(stat = "identity", 
  position = "fill")

shapeplot + theme_classic() +
  scale_fill_manual(name="Shape",
  labels = c("Pellet", "Sheet", "Microbead","Fragment", "Fibre"),
  values=c("#ffa600", "#ff6361", "#bc5090", "#58508d", "#003f5c")) +
  labs(y = "Proportion") +
  scale_x_discrete(labels = c("Mussels", "Sediment")) +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size=16), 
        axis.title.y = element_text(size=16),
        legend.text = element_text(size = 12),
        legend.title = element_text(size=14))
```

```{r FIBRE TYPES, include = FALSE}
#### SEDIMENT ####
fibre_s <- datS %>%
  subset(shape == "fibre") %>% 
  group_by(group_particle) %>% 
  tally(name = "fibrecount_sed") 

#### MUSSELS ####
fibre_m <- datM %>%
  subset(shape == "fibre") %>% 
  group_by(group_particle) %>% 
  tally(name = "fibrecount_mus") 

### BOTH SED AND MUS ###
fibre_sm <- full_join(fibre_m, fibre_s, by = "group_particle", na.rm=FALSE)
fibre_sm[is.na(fibre_sm)] <- 0

fibre_sm_long <- fibre_sm %>%  ######## Changes to long format
  gather(key = "Matrix",
        value = "FibreCount", 
        -c(group_particle)) 


plot_fibre_sm <- ggplot(fibre_sm_long, 
  aes(x = Matrix, y = FibreCount, 
      fill = factor(group_particle, 
      levels = c("rubber", "acrylic", "polyethylene","nylon", "polyester", "cellulose")))) +
  theme_classic() +              
  geom_bar(stat = "identity",
      position = "fill") + 
  scale_fill_manual(name="Plastic Type",
      labels = c("Rubber", "Acrylic", "Polyethylene","Nylon", "Polyester"),
      values=c("#ffa600", "#ff6361", "#bc5090", "#58508d", "#003f5c")) +
  labs(y = "Proportion") +
  scale_x_discrete(labels = c("Mussels", "Sediment")) +
  theme(axis.text.x = element_text(size = 12),
      axis.text.y = element_text(size = 12),
      axis.title.x = element_text(size=16), 
      axis.title.y = element_text(size=16),
      legend.text = element_text(size = 12),
      legend.title = element_text(size=14))

##   position = position_dodge(width=0.9))

```
